A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-19 tex/body.tex
more

Strictly speaking, normal interpretations are not models of codatatypes,
because they are restricted to an $\omega$-regular values, whereas models must
also cater for acyclic infinite terms. However, by monotonicity of ground
constraints, it is trivial to extend a normal interpretation into a model.
In the following, we focus on normal interpretations.

When constructing a model $\M$ for $\Ec$,
it remains only to specify how $\M$ interprets wrongly applied selector terms and variables.
For the latter, this will be based on the mapping $\Val$ computed in phase~2 of the calculus.

>>>>

Strictly speaking, normal interpretations are not models of codatatypes,
because they are restricted to an $\omega$-regular values, whereas actual models must
also cater for acyclic infinite terms. However, by monotonicity of ground
constraints, it is trivial to extend a normal interpretation to an actual model.
In the following, we focus on the former and unapologetically call them
models.

When constructing a model $\M$ of $\Ec$,
it remains only to specify how $\M$ interprets wrongly applied selector terms and variables.
For the latter, this will be based on the mapping $\Val$ computed in phase~2 of the calculus.
